The imprint of global magma oceans on exoplanet demographics

### 2023-03-29 src/tex/ms.tex
clarify why M dwarfs are key

\textit{Size and composition of the planetary sample}: Evidently, the significance of a statistical trend increases with a larger sample size. In addition, the sample must include planets on both sides of the instellation threshold, which is only sufficiently given for low-mass host stars.

>>>>

\textit{Size and composition of the planetary sample}: Evidently, the significance of a statistical trend increases with a larger sample size. In addition, the sample must include planets on both sides of the instellation threshold, which, due to the strongly distance-dependent detection bias associated with the transit method, is only sufficiently given for low-mass host stars.
